---
title: "Kapitel 3) Dynamische Faktormodelle und Hauptkomponenten"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
editor_options:
  chunk_output_type: console
---

# Setup

```{r}
# Optionen Rendering
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r}
# Säubere Umgebung
rm(list=ls())

# Lade Pakete
library(zoo)
library(dynlm)
library(sandwich)
library(lmtest)
library(urca)
library(AER)
library(scales)
library(R.matlab)

# Lade helper functions
source(rprojroot::find_rstudio_root_file("02-code/dfm_functions.r"))
```

# Kapitel 3) Dynamische Faktormodelle und Hauptkomponenten

## Datenaufbereitung

```{r}
#..................................................
# Load data and estimated factors ----

# Load observable macro variables
macro.01.dat <- read.table(rprojroot::find_rstudio_root_file("03-daten/us_macro_data.txt"),
                           header = TRUE,
                           sep = ",",
                           colClasses = c("character", "numeric", "numeric", "numeric"))

macro.01.ts <- ts(macro.01.dat[,-c(1)], frequency = 4, start = c(1955, 2), end = c(2017, 4))
```

```{r}
#..................................................
# Load all observable macro variables: The data are provided by S&W in a matlab matrix, datain.mat

tmp <- readMat(con = rprojroot::find_rstudio_root_file("03-daten/datain.mat"))

bpdata_raw <- tmp$datain[1,1,1]$bpdata.raw
bpdata <- tmp$datain[2,1,1]$bpdata # use this for estimation
bpdata_noa <- tmp$datain[3,1,1]$bpdata.noa
bpnamevec <- tmp$datain[4,1,1]$bpnamevec
bplabvec.long <- tmp$datain[5,1,1]$bplabvec.long
bplabvec.short <- tmp$datain[6,1,1]$bplabvec.short
bpoutliervec <- tmp$datain[7,1,1]$bpoutliervec
bptcodevec <- tmp$datain[8,1,1]$bptcodevec
bpcatcode <- tmp$datain[9,1,1]$bpcatcode
bpinclcode <- tmp$datain[10,1,1]$bpinclcode # use this for estimation
calvec <- tmp$datain[11,1,1]$calvec
calds <- tmp$datain[12,1,1]$calds
dnobs <- tmp$datain[13,1,1]$dnobs

# Transform to time series
macro.02.dat <- bpdata

macro.02.ts <- ts(macro.02.dat, frequency = 4, start = c(1959, 1), end = c(2017, 4))
colnames(macro.02.ts) <- paste0("V", seq(1,ncol(macro.02.ts)))
```

### Schätzung der unbeobachtbaren Faktoren

Basierend auf allen Makro Variablen.

```{r, cache=TRUE}
#..................................................
# Estimate unobserved factors based on all macro variables ----

# determine the start and end of period for factor estimation
# dat.seq <- seq.Date(from = as.Date("1955-04-01"), to = as.Date("2017-10-01"), by = "quarter")
dat.seq <- seq.Date(from = as.Date("1959-01-01"), to = as.Date("2017-10-01"), by = "quarter")

# dat.tmp <- window(macro.02.ts, start = c(1955, 4), end = c(2014, 1))
dat.tmp <- window(macro.02.ts, start = c(1959, 1), end = c(2017, 4))
xdata <- matrix(as.vector(dat.tmp), nrow = nrow(dat.tmp), ncol = ncol(dat.tmp)) # transform to "matrix"/"array"

# factor estimation using variables without missing values based on PCA

# fa based on ordinary pca
X <- as.matrix(scale(packr(xdata), center = TRUE, scale = FALSE))
n.fac <- 4

# based on svd directly
sv <- svd(X)
scores <- X %*% sv$v
F.est <- scores[,1:n.fac]

factor.est.pca <- F.est
factor.est.pca.ts <- ts(factor.est.pca, frequency = 4, start = c(1959, 1), end = c(2017, 4))

# factor estimation using all variables based on iterative LS
factor.est.ite <- factor_estimation_ls(xdata = xdata, n.fac = 4, nt.min = 20, init = "svd")
factor.est.ite.ts <- ts(factor.est.ite$fac, frequency = 4, start = c(1959, 1), end = c(2017, 4))

#..................................................
# Merge time series ----

# use some date sequence as basis for ts
date <- ts(seq.Date(from = as.Date("1950-01-01"), to = as.Date("2025-01-01"), by = "quarter"), frequency = 4, start = c(1950, 1), end = c(2025,1))
TT <- length(date)

# merge all variables/factors
data.all.ts <- cbind(date, macro.01.ts, macro.02.ts, factor.est.pca.ts, factor.est.ite.ts) # based on estimated factors

# extract time period of interest
data.all.ts <- window(data.all.ts, start = c(1959, 1), end = c(2017, 4))
# corresponding date
date <- seq.Date(from = as.Date("1959-01-01"), to = as.Date("2017-10-01"), by = "quarter")
```

### FAVAR Analyse No 01

Nicht-rekursive Schätzung der Faktoren auf der Grundlage von Variablen ohne fehlende Werte

```{r, cache=TRUE}
#..................................................
# A 1) Unfair analysis on variables without missing values ----

# A 1.1) h=1 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 1

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
F1 <- as.numeric(data.all.ts[,136])
F2 <- as.numeric(data.all.ts[,137])
F3 <- as.numeric(data.all.ts[,138])
F4 <- as.numeric(data.all.ts[,139])

data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      F1_h_l1 = lag_fun(F1, h),
                      F2_h_l1 = lag_fun(F2, h),
                      F3_h_l1 = lag_fun(F3, h),
                      F4_h_l1 = lag_fun(F4, h),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- NULL

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_01_h1_poos_diagnosen.txt")
FVAR.POOS.r4.h1.01 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 1, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h1.01$RMSFE.POOS

# A 1.2) h=4 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 4

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
F1 <- as.numeric(data.all.ts[,136])
F2 <- as.numeric(data.all.ts[,137])
F3 <- as.numeric(data.all.ts[,138])
F4 <- as.numeric(data.all.ts[,139])

data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      F1_h_l1 = lag_fun(F1, h),
                      F2_h_l1 = lag_fun(F2, h),
                      F3_h_l1 = lag_fun(F3, h),
                      F4_h_l1 = lag_fun(F4, h),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- NULL

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_01_h4_poos_diagnosen.txt")
FVAR.POOS.r4.h4.01 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 4, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h4.01$RMSFE.POOS

# A 1.3) h=8 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 8

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
F1 <- as.numeric(data.all.ts[,136])
F2 <- as.numeric(data.all.ts[,137])
F3 <- as.numeric(data.all.ts[,138])
F4 <- as.numeric(data.all.ts[,139])

data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      F1_h_l1 = lag_fun(F1, h),
                      F2_h_l1 = lag_fun(F2, h),
                      F3_h_l1 = lag_fun(F3, h),
                      F4_h_l1 = lag_fun(F4, h),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- NULL

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_01_h8_poos_diagnosen.txt")
FVAR.POOS.r4.h8.01 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 8, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h8.01$RMSFE.POOS
```

### FAVAR Analyse No 02

Nicht-rekursive Schätzung der Faktoren auf der Grundlage aller Variablen (vgl. S&W, 2020, Tabelle 17.3, Zeile 3)

```{r, cache=TRUE}
#..................................................
# A 2) Unfair analysis based on all observations ----

# A 2.1) h=1 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 1

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
F1 <- as.numeric(data.all.ts[,140])
F2 <- as.numeric(data.all.ts[,141])
F3 <- as.numeric(data.all.ts[,142])
F4 <- as.numeric(data.all.ts[,143])

data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      F1_h_l1 = lag_fun(F1, h),
                      F2_h_l1 = lag_fun(F2, h),
                      F3_h_l1 = lag_fun(F3, h),
                      F4_h_l1 = lag_fun(F4, h),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- NULL

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_02_h1_poos_diagnosen.txt")
FVAR.POOS.r4.h1.02 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 1, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h1.02$RMSFE.POOS

# A 2.2) h=4 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 4

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
F1 <- as.numeric(data.all.ts[,140])
F2 <- as.numeric(data.all.ts[,141])
F3 <- as.numeric(data.all.ts[,142])
F4 <- as.numeric(data.all.ts[,143])

data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      F1_h_l1 = lag_fun(F1, h),
                      F2_h_l1 = lag_fun(F2, h),
                      F3_h_l1 = lag_fun(F3, h),
                      F4_h_l1 = lag_fun(F4, h),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- NULL

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_02_h4_poos_diagnosen.txt")
FVAR.POOS.r4.h4.02 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 4, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h4.02$RMSFE.POOS

# A 2.3) h=8 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 8

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
F1 <- as.numeric(data.all.ts[,140])
F2 <- as.numeric(data.all.ts[,141])
F3 <- as.numeric(data.all.ts[,142])
F4 <- as.numeric(data.all.ts[,143])

data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      F1_h_l1 = lag_fun(F1, h),
                      F2_h_l1 = lag_fun(F2, h),
                      F3_h_l1 = lag_fun(F3, h),
                      F4_h_l1 = lag_fun(F4, h),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- NULL

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_02_h8_poos_diagnosen.txt")
FVAR.POOS.r4.h8.02 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 8, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h8.02$RMSFE.POOS
```

### FAVAR Analyse No 03

Rekursive Schätzung der Faktoren auf der Grundlage von Variablen ohne fehlende Werte.

```{r, cache=TRUE}
#..................................................
# A 3) Fair analysis based on variables without missing values ----

# A 3.1) h=1 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 1

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- data.all.ts[,which(colnames(data.all.ts) %in% paste0("macro.02.ts.V", seq(1,ncol(macro.02.ts))))]
colnames(data.03) <- paste0("V", seq(1,ncol(data.03)))

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_03_h1_poos_diagnosen.txt")
FVAR.POOS.r4.h1.03 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 1, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = FALSE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h1.03$RMSFE.POOS

# A 3.2) h=4 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 4

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- data.all.ts[,which(colnames(data.all.ts) %in% paste0("macro.02.ts.V", seq(1,ncol(macro.02.ts))))]
colnames(data.03) <- paste0("V", seq(1,ncol(data.03)))

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_03_h4_poos_diagnosen.txt")
FVAR.POOS.r4.h4.03 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 4, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = FALSE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h4.03$RMSFE.POOS

# A 3.3) h=8 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 8

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- data.all.ts[,which(colnames(data.all.ts) %in% paste0("macro.02.ts.V", seq(1,ncol(macro.02.ts))))]
colnames(data.03) <- paste0("V", seq(1,ncol(data.03)))

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_03_h8_poos_diagnosen.txt")
FVAR.POOS.r4.h8.03 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 8, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = FALSE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h8.03$RMSFE.POOS
```

### FAVAR Analyse No 04

Rekursive Schätzung der Faktoren auf der Grundlage aller Variablen

```{r, cache=TRUE}
#..................................................
# A 4) Fair analysis based on all variables ----

# A 4.1) h=1 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 1

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- data.all.ts[,which(colnames(data.all.ts) %in% paste0("macro.02.ts.V", seq(1,ncol(macro.02.ts))))]
colnames(data.03) <- paste0("V", seq(1,ncol(data.03)))

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_04_h1_poos_diagnosen.txt")
FVAR.POOS.r4.h1.04 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 1, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h1.04$RMSFE.POOS

# A 4.2) h=4 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 4

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- data.all.ts[,which(colnames(data.all.ts) %in% paste0("macro.02.ts.V", seq(1,ncol(macro.02.ts))))]
colnames(data.03) <- paste0("V", seq(1,ncol(data.03)))

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_04_h4_poos_diagnosen.txt")
FVAR.POOS.r4.h4.04 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 4, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h4.04$RMSFE.POOS

# A 4.3) h=8 ----

# dates data frame (date column is important!)
date.df <- data.frame(date = date,
                      year = format(date, "%Y"),
                      quarter = quarters(date),
                      month = format(date, "%m"),
                      day = format(date, "%d"))

# target variable (data frame)
GDP <- as.numeric(data.all.ts[,2])
h <- 8

data.01 <- data.frame(GDPGR_h = (400/h) * (log(GDP / lag_fun(GDP, h))))

# observed predictors (variables) (data frame)
data.02 <- data.frame(GDPGR_h_l1 = lag_fun(log(GDP / lag_fun(GDP, 1)), h),
                      GDPGR_h_l2 = lag_fun(log(GDP / lag_fun(GDP, 1)), h + 1),
                      CONST = 1)

# observed predictors for (fair) construction of unobserved factors (matrix/array)
data.03 <- data.all.ts[,which(colnames(data.all.ts) %in% paste0("macro.02.ts.V", seq(1,ncol(macro.02.ts))))]
colnames(data.03) <- paste0("V", seq(1,ncol(data.03)))

log.file <- rprojroot::find_rstudio_root_file("05-ergebnisse/favar_04_h8_poos_diagnosen.txt")
FVAR.POOS.r4.h8.04 <- FVAR_POOS_function(date.df = date.df, data.01 = data.01, data.02 = data.02, data.03 = data.03, h = 8, n.fac = 4, fre = "quarter",
                                         all.per.sta = as.Date("1981-01-01"), all.per.end = as.Date("2017-10-01"),
                                         est.per.sta = as.Date("1981-01-01"), est.per.end = as.Date("2002-10-01"),
                                         pre.per.sta = as.Date("2002-10-01"), pre.per.end = as.Date("2017-10-01"),
                                         mis.val = TRUE, print = TRUE, log.file = log.file)
FVAR.POOS.r4.h8.04$RMSFE.POOS
```

### Vergleich Ergebnisse

```{r, echo=FALSE}
#..................................................
# Comparison of results ----

print("..................................................")
print("Non-Recursive Estimation of the Factors based on variables without missing values")

print("FVAR.POOS.r4.h1.01$RMSFE.POOS")
FVAR.POOS.r4.h1.01$RMSFE.POOS
print("FVAR.POOS.r4.h4.01$RMSFE.POOS")
FVAR.POOS.r4.h4.01$RMSFE.POOS
print("FVAR.POOS.r4.h8.01$RMSFE.POOS")
FVAR.POOS.r4.h8.01$RMSFE.POOS

print("..................................................")
print("Non-Recursive Estimation of the Factors based on all variables (see: S&W, 2020, table 17.3, row 3)")

print("FVAR.POOS.r4.h1.02$RMSFE.POOS")
FVAR.POOS.r4.h1.02$RMSFE.POOS
print("FVAR.POOS.r4.h4.02$RMSFE.POOS")
FVAR.POOS.r4.h4.02$RMSFE.POOS
print("FVAR.POOS.r4.h8.02$RMSFE.POOS")
FVAR.POOS.r4.h8.02$RMSFE.POOS

print("..................................................")
print("Recursive Estimation of the Factors based on variables without missing values")

print("FVAR.POOS.r4.h1.03$RMSFE.POOS")
FVAR.POOS.r4.h1.03$RMSFE.POOS
print("FVAR.POOS.r4.h4.03$RMSFE.POOS")
FVAR.POOS.r4.h4.03$RMSFE.POOS
print("FVAR.POOS.r4.h8.03$RMSFE.POOS")
FVAR.POOS.r4.h8.03$RMSFE.POOS

print("..................................................")
print("Recursive Estimation of the Factors based on all variables")

print("FVAR.POOS.r4.h1.04$RMSFE.POOS")
FVAR.POOS.r4.h1.04$RMSFE.POOS
print("FVAR.POOS.r4.h4.04$RMSFE.POOS")
FVAR.POOS.r4.h4.04$RMSFE.POOS
print("FVAR.POOS.r4.h8.04$RMSFE.POOS")
FVAR.POOS.r4.h8.04$RMSFE.POOS
```

